Image Processing for Discovering\\ the Rules of Video Games

### 2018-04-16 proposal/paper.tex
Bibliography references added to paper

>>>>

\bibitem{5}
	J. Bradberry, “Introduction to Monte Carlo Tree Search”, 2015. Available: https://jeffbradberry.com/posts/2015/09/intro-to-monte-carlo-tree-search/

\bibitem{6}
	Harrison, “Using a neural network to solve OpenAI's CartPole balancing environment”, 2017. Available: https://pythonprogramming.net/openai-cartpole-neural-network-example-machine-learning-tutorial

\bibitem{7}
	J. Levine, “Monte Carlo Tree Search”, 2017. Available: https://www.youtube.com/watch?v=UXW2yZndl7U

\bibitem{8}
		K. Stanley, R. Miikkulainen, "Evolving Neural Networks through Augmenting Topologies", The MIT Press Journals, 2002. Available: http://nn.cs.utexas.edu/downloads/papers/stanley.ec02.pdf
